\documentclass[margin,centered]{resume}
\usepackage{fancyhdr}  % use this package to get a 2 line header
\usepackage[utf8]{inputenc}
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it Hannah Alpert-Abrams}\\{\it p. \thepage} } % right-side header
\cfoot{} % the foot is empty
\usepackage[T1]{fontenc}
\renewcommand{\labelitemi}{$-$}
\renewcommand{\labelitemii}{$\cdot$}


\newcommand{\pubtitle}[1]{\textsl{#1}}
\newcommand{\employerName}[1]{\textbf{#1}}
\newcommand{\jobPosition}[1]{\textit{#1}}
\newcommand{\subtitle}[1]{\textbf{#1}}

%______________________________________________________________
\begin{document}
\thispagestyle{empty} % this page has no header  
\name{\huge \centerline{\textsc{Hannah Alpert-Abrams}} \\
  \centerline{\rule{\textwidth}{0.5mm}}
}
\address{halperta@gmail.com}
\begin{resume}

%\moveleft.5\hoffset\centerline{\LARGE\textbf{{Hannah Alpert-Abrams}}}
%\hrule

    \vspace{5mm}

    %____________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

    I study twentieth century literature of the Americas. I am interested in archival studies, cultural studies, translation, and book history. My research focuses on popular representations of Mexican indigeneity and the Spanish conquest of Mexico across the U.S./Mexico border.


    \vspace{0mm}

    %____________________________________________________________
    % Education
    \section{\mysidestyle Education}

    {\employerName{The University of Texas at Austin}}\\
	{\sl Ph.D.}, Comparative Literature ~(in progress) \hfill Aug 2013 - Present\\
    {\sl M.A.}, Comparative Literature \hfill Aug 2011 - May 2013 \\
    Masters Thesis: \pubtitle{El Tony Manero Nacional}\\
    
    \employerName{Oberlin College}\\
	{\sl B.A.}, English, \emph{Summa Cum Laude}, \hfill Aug 2003 - May 2007 \\ 
	{\sl Universidad de Belgrano (Buenos Aires, Argentina)\hfill Spring 2006}\\

    \vspace{-2mm}

    %____________________________________________________________
    % Papers and Publications
    \section{\mysidestyle Papers and Publications}
	
	{\subtitle{Academic Papers}}
	
    \textsl{Hybrid Romances in Borges and Baudelaire} \\
    American Comparative Literature Association: Toronto, April 2013 

    \textsl{Translating an Unreadable Novel: The Lost Steps in the United States} \\
    Pterod\'{a}ctilo 11: Fall 2012 

    \textsl{Drunken Archives} \\
    Graduate Association of Comparative Literature Conference: UT Austin, 2012
	
	{\subtitle{Book Reviews}}\\
	\textsl{Kathryn Burns: Into the Archive}\\ 
    Sequels: Forthcoming: 2014 \\
    \vspace{2mm}

    \textsl{Mart\'{i}n Ad\'{a}n: The Cardboard House}\\ 
    Full Stop: 21 November 2013 \\
    \vspace{-2mm}

    %____________________________________________________________
    % Professional Experience
    \section{\mysidestyle Teaching}

    \employerName{The University of Texas at Austin}\\
    \jobPosition{Assistant Instructor} \hfill Aug 2013 - Present \\
    Rhetoric and Composition (RHE 306)
    \begin{itemize}  \itemsep -2pt
        \item Instructor for introductory-level college course in rhetoric and composition. Customize syllabus, design lesson plans and assignments, build website, grade papers. Staff the undergraduate drop-in writing center.
    \end{itemize}
	\vspace{1mm}
	
    \jobPosition{Teaching Assistant} \hfill Aug 2011 - May 2013 \\
    Masterworks of English Literature (E316K)
    \begin{itemize}  \itemsep -2pt
        \item Led discussion sections for sophomore-level English course. % Worked with up to fifty students each semester to develop reading and writing skills. 
		%\item Proctored and graded quizzes, exams, and essays.
    \end{itemize}
    \vspace{1mm}
	
	{\employerName{The Centre for Creativity in Education and Cultural Heritage}}\hfill Jerusalem, Israel\\
    \jobPosition{Program Associate} \hfill Spring 2009 \\
    \begin{itemize}  \itemsep -2pt
        \item Grant writing, web development, classroom support and curriculum development for a folklore and co-existence program. 
    \end{itemize}
    \vspace{1mm}
	
	{\employerName{The Chewonki Foundation}}\hfill Wiscassett, Maine\\
    \jobPosition{Environmental Educator/Trip Leader} \hfill 2008 \\
    \begin{itemize}  \itemsep -2pt
        \item Taught ecology and outdoor living skills to school groups during three- to five-day overnight encampments. 
		%\item Led four- to ten-day wilderness trips in salt-water canoeing, sea kayaking, and backpacking.
    \end{itemize}
    \vspace{1mm}
	
	{\employerName{SITES: Spanish in the Elementary Schools}}\hfill Oberlin, Ohio\\
    \jobPosition{Instructor and Teaching Assistant} \hfill Oct 2006 - May 2007 \\
    \begin{itemize}  \itemsep -2pt
        \item Co-taught Spanish twice weekly to a third-grade class. Tutored English as a second language. 
	    \item Co-authored preliminary SITES curriculum.
    \end{itemize}
    \vspace{1mm}
	
	{\employerName{Oberlin College English Department}}\hfill Oberlin, Ohio\\
    \jobPosition{Writing Associate} \hfill 2005 - 2007 \\
    \begin{itemize}  \itemsep -2pt
        %\item Worked individually on writing skills with students in introductory English courses.
	    \item Tutored in drop-in writing center for students across disciplines.
    \end{itemize}
    \vspace{1mm}
	
\section{\mysidestyle Research and Writing}
	
    {\employerName{Idea Platforms, Inc.}}\hfill Concord, MA\\
    \jobPosition{Content Architect} \hfill Oct 2009 - May 2011 \\
    \begin{itemize}  \itemsep -2pt 
    	\item Worked with a book-production team to develop and write idea-driven, popular non-fiction.
    	\item Drafted proposals, book chapters, and manuscripts in collaboration with authors. Projects included: \emph{The Emotional Calendar} (Times Books 2010), \emph{A Higher Ambition} (Harvard Business Press, 2011), \emph{Better Than Normal} (Random House, 2013).
		\item Conducted interviews and research on book-related content.
		\item Led a team of researchers and writers to develop books.
    	\end{itemize} 
    \vspace{1mm}

    {\employerName{Oberlin College}}\hfill Oberlin, Ohio\\
    \jobPosition{Research Assistant: Professor Ana Cara} \hfill Summer 2007 \\
    \begin{itemize}  \itemsep -2pt 
    	\item Independently designed and implemented research in ethnology and literary theory for an academic publication on Argentine author Jorge Luis Borges. 
	    \item Wrote research summaries, reports and analysis.  
    \end{itemize} 
	    \vspace{1mm}
     
    {\employerName{Florida State University}}\hfill Tallahassee, Florida\\
    \jobPosition{Myrmecology Intern: Dr. Walter Tschinkel} \hfill Jan 2005 \\
    \begin{itemize}  \itemsep -2pt 
    	\item Prepared plots and collected data for studies of invasive fire ant species.
    \end{itemize} 
	\vspace{1mm}
	
%	{\employerName{La Selva Biological Reserve}}\hfill Costa Rica \\
%    \jobPosition{Ecology Intern: Dr. Robin Chazdon} \hfill Summer 2004
%    \begin{itemize}  \itemsep -2pt 
%    	\item Ran transects, worked on red/farred data collection and insect identification
%    \end{itemize} 
%	\vspace{1mm}
	
    \vspace{0mm}

    %____________________________________________________________
%    % Honors and Awards
    \section{\mysidestyle Honors and Awards} 

%   {\sl Graduate}\\
   \textsl{SHARP-CalRBS Scholarship:} \emph{History of the Book in Hispanic America} - Summer 2013
   \textsl{Amy Adina Schulman Memorial Fund Grant:} \emph{Centre for Creativity in Education and Cultural Heritage} - Spring 2009
    \textsl{Dudley B. Tenney English Literature Prize:} \emph{For Excellence in Math and Natural Science} - Spring 2007

%   \vspace{0mm}

    %____________________________________________________________
    % Service and Activities
    \section{\mysidestyle Academic Service}

    \textbf{Graduate Association in Comparative Literature:} Conference Co-Organizer (2013); Conference Associate (2012)\\
    \textbf{Bat City Review:} Fiction Co-Editor (2013); Associate Fiction Editor (2012)\\
	\textbf{Institute for Days Spent Making:} Program Organizer (2013)\\
	\textbf{Blogging:} Full-Stop.net; blog.pterodactilo.com\\
    %____________________________________________________________
    % Skills and Certifications
%    \section{\mysidestyle Skills and Certifications}
%
%    \textbf{Languages:} English, Spanish, French \\
%    \textbf{Certifications:} Wilderness First Responder (exp. 2013); ARC First Aid, CPR, Lifeguarding; Chainsaw Safety
            

    \vspace{2mm}

%____________________________________________________________
\end{resume}
\end{document}

